Analysis of split plot design using lme4

### 2017-08-02 lme4_analysis.Rmd
TShSB Incidence didn't run interactions
Fix that issue. Now runs WMGT * NRTE not WMGT + NRTE

```{r 2015_TShB_incidence}
library(lme4)
library(lsmeans)
TShB_inc_AUDPS <- lmer(TShB_inc_AUDPS ~ WMGT + NRTE + (1|REP), data = AUDPS_2015)
summary(TShB_inc_AUDPS)

@@

```{r 2016_TShB_incidence}
TShB_inc_AUDPS <- lmer(TShB_inc_AUDPS ~ WMGT + NRTE + (1|REP), data = AUDPS_2016)
summary(TShB_inc_AUDPS)

>>>>

```{r 2015_TShB_incidence}
library(lme4)
library(lsmeans)
TShB_inc_AUDPS <- lmer(TShB_inc_AUDPS ~ WMGT * NRTE + (1|REP), data = AUDPS_2015)
summary(TShB_inc_AUDPS)

@@

```{r 2016_TShB_incidence}
TShB_inc_AUDPS <- lmer(TShB_inc_AUDPS ~ WMGT * NRTE + (1|REP), data = AUDPS_2016)
summary(TShB_inc_AUDPS)
